---
title: "Final Project for 1675"
subtitle: "Exploring the Data"
author: "David Spellman"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load_tidyverse}
library(tidyverse)
```

```{r, read_final_data}
df <- readr::read_csv("cs_1675_fall2021_finalproject.csv", col_names = TRUE)
```

### Take an initial look at the data and some basic statistics

```{r, show_data_glimpse}
df %>% glimpse ()
df %>% summary ()
stats <- tibble::tibble (variable = names (df), num_missing = map_dbl (df, ~ sum (is.na (.))), num_unique = map_dbl (df, n_distinct), min_value = map_dbl (df, min), median_value = map_dbl (df, median), max_value = map_dbl (df, max))
stats %>% knitr::kable (caption = "variables overview")
df %>% select (- output) %>% distinct () %>% dim ()
```

### First visualize the distributions of the data. 

```{r, viz_replicated_striplot_mean}
dfT %>% 
  left_join(df_configs,
            by = input_names) %>% 
  filter(num_rows > 1) %>% 
  ggplot(mapping = aes(x = as.factor(set_id), y = output)) +
  stat_summary(geom = 'linerange',
               fun.min = min, fun.max = max,
               mapping = aes(group = set_id),
               color = 'grey', size = 1.1) +
  geom_point() +
  stat_summary(fun.data = 'mean_se',
               color = 'red',
               mapping = aes(group = set_id),
               fun.args = list(mult = 2)) +
  geom_hline(yintercept = range(dfT$output),
             color = 'grey', linetype = 'dashed', size = 1.2) +
  theme_bw()
```

```{r, make_my_dfT_dfT}
my_dfT <- dfT %>% 
  group_by(across(dfT:m)) %>% 
  summarise(output = mean(output),
            .groups = 'drop')
```

```{r, check_ready_rows}
my_dfT %>% dim()

nrow(my_dfT) < nrow(dfT)
```

```{r, viz_all_hist}
my_dfT %>% 
  tibble::rowid_to_column() %>% 
  pivot_longer(!c("rowid")) %>% 
  ggplot(mapping = aes(x = value)) +
  geom_histogram(bins = 31) +
  facet_wrap(~name, scales = "free") +
  theme_bw() +
  theme(axis.text.y = element_blank())
```

```{r, viz_z_bar}
my_dfT %>% 
  ggplot(mapping = aes(x = as.factor(z))) +
  geom_bar(mapping = aes(y = stat(prop),
                         group = 1)) +
  geom_text(stat = 'count',
            mapping = aes(y = after_stat( count / sum(count) ),
                          label = after_stat( signif(count / sum(count), 3) )),
            color = 'red', nudge_y = 0.01, size = 3) +
  theme_bw()
```

### First we will graph the response in respect to each of the x inputs. 

``` {r, plot_output_in_terms_of_x1}
df %>% ggplot (mapping = aes (x = x1, y = output)) + geom_point () + geom_smooth (method = lm)
```

### Based on this graph it looks like the response becomes worse as x1 becomes greater
### The best x1 values based on this graph seem to fall between 0.1 to 0.3

``` {r, plot_output_in_terms_of_x2}
df %>% ggplot (mapping = aes (x = x2, y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_x3}
df %>% ggplot (mapping = aes (x = x3, y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_x4}
df %>% ggplot (mapping = aes (x = x4, y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now for calculating and plotting the x5 calculated input, as well as calculating w, t, and z for other plots.

``` {r, calculate_x5_w_z_t_and_plot_output_in_terms_of_x5}
### calculate x5, z, w, and t.
dfT <- (df %>% tibble::as_tibble () %>% mutate (x5 = (1 - (x1 + x2 + x3 + x4)), w = (x2 / (x3 + x4)), z = ((x1 + x2) / (x4 + x5)), t = (v1 * v2)))

### plot output against x5
dfT %>% ggplot (mapping = aes (x = x5, y = output)) + geom_point () + geom_smooth (method = lm)
```

### Visualizing calculated w input. 

``` {r, plot_output_in_terms_of_w}
dfT %>% ggplot (mapping = aes (x = w, y = output)) + geom_point () + geom_smooth (method = lm)
```

### Visualizing calculated z input. 

``` {r, plot_output_in_terms_of_z}
dfT %>% ggplot (mapping = aes (x = z, y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now we will graph the response in respect to each of the v inputs. 

``` {r, plot_output_in_terms_of_v1}
df %>% ggplot (mapping = aes (x = v1, y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v2}
df %>% ggplot (mapping = aes (x = v2, y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v3}
df %>% ggplot (mapping = aes (x = v3, y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v4}
df %>% ggplot (mapping = aes (x = v4, y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v5}
df %>% ggplot (mapping = aes (x = v5, y = output)) + geom_point () + geom_smooth (method = lm)
```

### Plotting the output in terms of the calculated t input. 

``` {r, plot_output_in_terms_of_t}
dfT %>% ggplot (mapping = aes (x = t, y = output)) + geom_point () + geom_smooth (method = lm)
```

### Try the same graphs above but now binned by machine used to produce mixture. 

### First we will graph the response in respect to each of the x inputs as before. 

``` {r, plot_output_in_terms_of_x1}
df %>% ggplot (mapping = aes (x = x1, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_x2}
df %>% ggplot (mapping = aes (x = x2, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_x3}
df %>% ggplot (mapping = aes (x = x3, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_x4}
df %>% ggplot (mapping = aes (x = x4, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Now for visualizing the inputs derived by the x inputs binned by machine.

``` {r, plot_output_in_terms_of_x5}
dfT %>% ggplot (mapping = aes (x = x5, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Visualizing calculated w input binned by machine. 

``` {r, plot_output_in_terms_of_w}
dfT %>% ggplot (mapping = aes (x = w, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Visualizing calculated z input binned by machine. 

``` {r, plot_output_in_terms_of_z}
dfT %>% ggplot (mapping = aes (x = z, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Now we will graph the response in respect to each of the v inputs. 

``` {r, plot_output_in_terms_of_v1}
df %>% ggplot (mapping = aes (x = v1, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v2}
df %>% ggplot (mapping = aes (x = v2, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v3}
df %>% ggplot (mapping = aes (x = v3, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v4}
df %>% ggplot (mapping = aes (x = v4, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v5}
df %>% ggplot (mapping = aes (x = v5, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Plotting the output in terms of the calculated t input binned by machine. 

``` {r, plot_output_in_terms_of_t}
dfT %>% ggplot (mapping = aes (x = t, y = output)) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Try plotting with logit transformation applied to the response. 

``` {r, plot_output_in_terms_of_x1}
df %>% ggplot (mapping = aes (x = x1, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_x2}
df %>% ggplot (mapping = aes (x = x2, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_x3}
df %>% ggplot (mapping = aes (x = x3, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_x4}
df %>% ggplot (mapping = aes (x = x4, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

### Now for calculating and plotting the x5 calculated input, as well as calculating w, t, and z for other plots.

``` {r, calculate_x5_w_z_t_and_plot_output_in_terms_of_x5}
### calculate x5, z, w, and t.
dfT <- (df %>% tibble::as_tibble () %>% mutate (x5 = (1 - (x1 + x2 + x3 + x4)), w = (x2 / (x3 + x4)), z = ((x1 + x2) / (x4 + x5)), t = (v1 * v2)))

### plot output against x5
dfT %>% ggplot (mapping = aes (x = x5, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

### Visualizing calculated w input. 

``` {r, plot_output_in_terms_of_w}
dfT %>% ggplot (mapping = aes (x = w, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

### Visualizing calculated z input. 

``` {r, plot_output_in_terms_of_z}
dfT %>% ggplot (mapping = aes (x = z, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

### Now we will graph the response in respect to each of the v inputs. 

``` {r, plot_output_in_terms_of_v1}
df %>% ggplot (mapping = aes (x = v1, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v2}
df %>% ggplot (mapping = aes (x = v2, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v3}
df %>% ggplot (mapping = aes (x = v3, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v4}
df %>% ggplot (mapping = aes (x = v4, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

``` {r, plot_output_in_terms_of_v5}
df %>% ggplot (mapping = aes (x = v5, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

### Plotting the output in terms of the calculated t input. 

``` {r, plot_output_in_terms_of_t}
dfT %>% ggplot (mapping = aes (x = t, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm)
```

### Now visualized the logistic response binned by machine as well. 

``` {r, plot_output_in_terms_of_x1}
df %>% ggplot (mapping = aes (x = x1, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_x2}
df %>% ggplot (mapping = aes (x = x2, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_x3}
df %>% ggplot (mapping = aes (x = x3, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_x4}
df %>% ggplot (mapping = aes (x = x4, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Now for visualizing the inputs derived by the x inputs binned by machine.

``` {r, plot_output_in_terms_of_x5}
dfT %>% ggplot (mapping = aes (x = x5, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Visualizing calculated w input binned by machine. 

``` {r, plot_output_in_terms_of_w}
dfT %>% ggplot (mapping = aes (x = w, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Visualizing calculated z input binned by machine. 

``` {r, plot_output_in_terms_of_z}
dfT %>% ggplot (mapping = aes (x = z, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Now we will graph the response in respect to each of the v inputs. 

``` {r, plot_output_in_terms_of_v1}
df %>% ggplot (mapping = aes (x = v1, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v2}
df %>% ggplot (mapping = aes (x = v2, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v3}
df %>% ggplot (mapping = aes (x = v3, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v4}
df %>% ggplot (mapping = aes (x = v4, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

``` {r, plot_output_in_terms_of_v5}
df %>% ggplot (mapping = aes (x = v5, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Plotting the output in terms of the calculated t input binned by machine. 

``` {r, plot_output_in_terms_of_t}
dfT %>% ggplot (mapping = aes (x = t, y = boot::logit (output))) + geom_point () + geom_smooth (method = lm) + facet_wrap (~m)
```

### Let's look for correlated features by looking at coupled interactions. 

### Let's start with plotting wx1 against the output to see if they are correlated. 

``` {r, check_wx1}
dfT %>% ggplot (mapping = aes (x = (w * x1), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now let's do the same check for x5w. 

``` {r, check_wx5}
dfT %>% ggplot (mapping = aes (x = (x5 * w), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now let's do the same check for the values used to calculate w: x2, x3, and x4. 

``` {r, check_wx2}
dfT %>% ggplot (mapping = aes (x = (x2 * w), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_wx3}
dfT %>% ggplot (mapping = aes (x = (x3 * w), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_wx4}
dfT %>% ggplot (mapping = aes (x = (x4 * w), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now check z for the same correlations. 

``` {r, check_zx1}
dfT %>% ggplot (mapping = aes (x = (x1 * z), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_zx2}
dfT %>% ggplot (mapping = aes (x = (x2 * z), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_zx3}
dfT %>% ggplot (mapping = aes (x = (x3 * z), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_zx4}
dfT %>% ggplot (mapping = aes (x = (x4 * z), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_zx5}
dfT %>% ggplot (mapping = aes (x = (x5 * z), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now check x5 against the other four x inputs. 

``` {r, check_x1x5}
dfT %>% ggplot (mapping = aes (x = (x1 * x5), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_x5x2}
dfT %>% ggplot (mapping = aes (x = (x2 * x5), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_x5x3}
dfT %>% ggplot (mapping = aes (x = (x3 * x5), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_x5x4}
dfT %>% ggplot (mapping = aes (x = (x4 * x5), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now let's check the interactions between the plain x inputs. 

``` {r, check_x1x2}
dfT %>% ggplot (mapping = aes (x = (x2 * x1), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_x1x3}
dfT %>% ggplot (mapping = aes (x = (x3 * x1), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_x1x4}
dfT %>% ggplot (mapping = aes (x = (x4 * x1), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now with x2 instead of x1. 

``` {r, check_x2x3}
dfT %>% ggplot (mapping = aes (x = (x3 * x2), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_x2x4}
dfT %>% ggplot (mapping = aes (x = (x4 * x2), y = x2)) + geom_point () + geom_smooth (method = lm)
```

### Now x3 in the interaction instead of x2. 

``` {r, check_x3x4}
dfT %>% ggplot (mapping = aes (x = (x4 * x3), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now to look for correlations among the v inputs. 

### Check for correlations between the derived t input and the five v inputs. 

``` {r, check_tv1}
dfT %>% ggplot (mapping = aes (x = (v1 * t), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_tv2}
dfT %>% ggplot (mapping = aes (x = (v2 * t), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_tv3}
dfT %>% ggplot (mapping = aes (x = (v3 * t), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_tv4}
dfT %>% ggplot (mapping = aes (x = (v4 * t), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_tv5}
dfT %>% ggplot (mapping = aes (x = (v5 * t), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now check v5 against the other four v inputs. 

``` {r, check_v1v5}
dfT %>% ggplot (mapping = aes (x = (v1 * v5), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_v5v2}
dfT %>% ggplot (mapping = aes (x = (v2 * v5), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_v5v3}
dfT %>% ggplot (mapping = aes (x = (v3 * v5), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_v5v4}
dfT %>% ggplot (mapping = aes (x = (v4 * v5), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now let's check the interactions between the plain v inputs. 

``` {r, check_v1v2}
dfT %>% ggplot (mapping = aes (x = (v2 * v1), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_v1v3}
dfT %>% ggplot (mapping = aes (x = (v3 * v1), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_v1v4}
dfT %>% ggplot (mapping = aes (x = (v4 * v1), y = output)) + geom_point () + geom_smooth (method = lm)
```

### Now with v2 instead of v1. 

``` {r, check_v2v3}
dfT %>% ggplot (mapping = aes (x = (v3 * v2), y = output)) + geom_point () + geom_smooth (method = lm)
```

``` {r, check_v2v4}
dfT %>% ggplot (mapping = aes (x = (v4 * v2), y = v2)) + geom_point () + geom_smooth (method = lm)
```

### Now v3 in the interaction instead of v2. 

``` {r, check_v3v4}
dfT %>% ggplot (mapping = aes (x = (v4 * v3), y = output)) + geom_point () + geom_smooth (method = lm)
```