---
title: "Part 4: Regression Models - Model 5"
author: "David Spellman"
date: "12/9/2021"
output: html_document
---

## Load packages
```{r, load_tidyverse}
library(tidyverse)
library(caret)
library(tidymodels)
```

## Read data

The code chunk below reads in the final project data.  

```{r, read_final_data}
df <- readr::read_csv("cs_1675_fall2021_finalproject.csv", col_names = TRUE)
```

The `readr::read_csv()` function displays the data types and column names associated with the data. However, a glimpse is shown below that reveals the number of rows and also shows some of the representative values for the columns.  

```{r, show_data_glimpse}
dft <- df %>% mutate(output=boot::logit(output))

bfm_df <- dft
bf_df <- bfm_df %>% select(-m)

efm_df <- dft %>% mutate(x5 = 1.0 - (x1+x2+x3+x4), w=x2/(x3+x4), z=(x1+x2)/(x4+x5), t=v1*v2)
ef_df <- efm_df %>% select(-m)

ef_df %>% glimpse()
```

```{r, build_data_frames}

classes <- (df$output < 0.33)
cdf <- df %>% mutate(Class=ifelse(classes, "good", "bad"))
cdf <- cdf %>% mutate(event=ifelse(classes, 1, 0))
cdf %>% glimpse()

cbfm_df <- bfm_df %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)
cbf_df <- bf_df  %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)
cefm_df <- efm_df  %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)
cef_df <- ef_df  %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)

```


You may use caret or tidymodels to handle the training, testing, and evaluation.
You must train and tune the following models:

```{r}
set.seed(2021)

cv_folds_bf <- vfold_cv(cbf_df, v = 5, repeats = 3, strata = Class)
cv_folds_bf

my_metrics <- metric_set(accuracy, roc_auc, mn_log_loss)
```

#Logistic regression:

#Regularized regression with Elastic net:

##1. Interact the categorical variable with all pair wise interactions of the continuous features.
  
```{r}
set.seed(2021)
my_ctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 5)
my_metric <- "Accuracy"

enet_p4_m5 <- train(Class~(x1+x2+x3+x4+x5+v1+v2+v3+v4+v5)^2:m,
                data = cefm_df,
                method = "glmnet",
                metric = my_metric,
                preProcess = c("center", "scale"),
                trControl = my_ctrl)

enet_p4_m5
```

```{r}
```

```{r}
enet_p4_m5 %>% readr::write_rds("part_4_model_5.rds")
```

```{r}
re_load_p4_m5 <- readr::read_rds("part_4_model_5.rds")
re_load_p4_m5 %>% summary()

library(ROCR)

p4_m5_prob <- predict(re_load_p4_m5, cefm_df, type = "prob")$good

p4_m5_perf <- prediction(p4_m5_prob, cefm_df$Class) %>%
  performance(measure = "tpr", x.measure = "fpr")

# Plot ROC curve
plot(p4_m5_perf, col = "black", lty = 2)
```


