---
title: "Part 4: Regression Models - Model 11"
author: "David Spellman"
date: "12/9/2021"
output: html_document
---

## Load packages
```{r, load_tidyverse}
library(tidyverse)
library(caret)
library(tidymodels)
```

## Read data

The code chunk below reads in the final project data.  

```{r, read_final_data}
df <- readr::read_csv("cs_1675_fall2021_finalproject.csv", col_names = TRUE)
```

The `readr::read_csv()` function displays the data types and column names associated with the data. However, a glimpse is shown below that reveals the number of rows and also shows some of the representative values for the columns.  

```{r, show_data_glimpse}
dft <- df %>% mutate(output=boot::logit(output))

bfm_df <- dft
bf_df <- bfm_df %>% select(-m)

efm_df <- dft %>% mutate(x5 = 1.0 - (x1+x2+x3+x4), w=x2/(x3+x4), z=(x1+x2)/(x4+x5), t=v1*v2)
ef_df <- efm_df %>% select(-m)

ef_df %>% glimpse()
```

```{r, build_data_frames}

classes <- (df$output < 0.33)
cdf <- df %>% mutate(Class=ifelse(classes, "good", "bad"))
cdf <- cdf %>% mutate(event=ifelse(classes, 1, 0))
cdf %>% glimpse()

cbfm_df <- bfm_df %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)
cbf_df <- bf_df  %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)
cefm_df <- efm_df  %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)
cef_df <- ef_df  %>% mutate(Class=ifelse(classes, "good", "bad")) %>% select(-output)

```


You may use caret or tidymodels to handle the training, testing, and evaluation.
You must train and tune the following models:

```{r}
set.seed(2021)

cv_folds_bf <- vfold_cv(cbf_df, v = 5, repeats = 3, strata = Class)
cv_folds_bf

my_metrics <- metric_set(accuracy, roc_auc, mn_log_loss)
```

#Logistic regression:

###Support Vector Machines (SVM)

```{r}
set.seed(2021)
my_ctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 5)
my_metric <- "Accuracy"

svmRadial_p4_m11 <- train(Class ~ .,
                 data = cefm_df,
                 method = "svmRadial",
                 metric = my_metric,
                 preProcess = c("center", "scale"),
                 trControl = my_ctrl)

svmRadial_p4_m11 %>% summary()
```

```{r}
library(ROCR)
plot_ROC <- function(model, df)
{
  model_prob <- predict(model, df, type = "prob")$good
  print (model_prob)
  
  preds <- prediction(model_prob, df$Class)
  print(preds)
  
  model_perf <- preds %>% performance(measure = "tpr", x.measure = "fpr")
  
  # Plot ROC curve
  plot(model_perf, col = "black")
  abline(a=0, b= 1, lty = 2)
}

```

```{r}
#modelRes <- plot_ROC(svmRadial_p4_m11, cefm_df)

# ROC using plotROC (ggplot2 extension)
#gc_prob <- predict(svmRadial_p4_m11, newdata = cefm_df %>% select(-Class), type = "prob")
#gc_pROC <- roc(response = gc$Class, predictor = gc_prob[, "good"])
#plot(gc_pROC)
#gc_pROC$auc

list(svmRadial_p4_m11)

#gc_prob_ex <- extractProb(list(svmRadial_p4_m11), cefm_df %>% select(-Class))
#gc_ggROC <- ggplot(gc_prob_ex, aes(d=obs, m=Good)) + geom_roc() 
#gc_ggROC_styled <- gc_ggROC +  annotate("text", x = .75, y = .25, 
#       label = paste("AUC =", round(calc_auc(gc_ggROC)$AUC, 2)))
#gc_ggROC_styled
```

```{r}
svmRadial_p4_m11 %>% readr::write_rds("part_4_model_11.rds")
```

```{r}
re_load_p4_m11 <- readr::read_rds("part_4_model_11.rds")
re_load_p4_m11 %>% summary()
```





