---
title: "Part 3: Regression Models - Model 5"
author: "David Spellman"
date: "12/9/2021"
output: html_document
---

## Load packages
```{r, load_tidyverse}
library(tidyverse)
library(tidymodels)
library(mltools)
library(caret)
```

## Read data

The code chunk below reads in the final project data.  

```{r, read_final_data}
df <- readr::read_csv("cs_1675_fall2021_finalproject.csv", col_names = TRUE)
```

The `readr::read_csv()` function displays the data types and column names associated with the data. However, a glimpse is shown below that reveals the number of rows and also shows some of the representative values for the columns.  

```{r, show_data_glimpse}
dft <- df %>% mutate(output=boot::logit(output))

bfm_df <- dft
bf_df <- bfm_df %>% select(-m)

efm_df <- dft %>% mutate(x5 = 1.0 - (x1+x2+x3+x4), w=x2/(x3+x4), z=(x1+x2)/(x4+x5), t=v1*v2)
ef_df <- efm_df %>% select(-m)

ef_df %>% glimpse()
```

#Regularized regression with Elastic net:

##5. Load model and regularize.
  
```{r}
re_load_lm_5 <- readr::read_rds("part_3_model_5.rds")
re_load_lm_5 %>% summary()
```

```{r}
penalty()
```

```{r}
mixture()
```

```{r}
my_lambda <- penalty(range = c(-10.5, 2), trans = log_trans())
my_alpha <- mixture(range = c(0.1, 1.0))
enet_grid <- grid_regular(my_lambda, my_alpha, 
                          levels = c(penalty = 75, mixture = 5))
enet_grid %>% glimpse()
```

```{r}
enet_spec <- linear_reg(penalty = tune(), mixture = tune()) %>% 
  set_engine("glmnet", 
             # glmnet specific options
             intercept = TRUE, standardize.response = TRUE, standardize = TRUE,
             path_values = exp(seq(-10.5, 2, length.out = 75)))
enet_spec %>% translate()
```

```{r}
p3_m5_recipe <- recipe (logit_response~., data = ef_df) %>%
  step_center(all_predictors()) %>% 
  step_scale(all_predictors()) %>%
  step_interact(terms=~ all_predictors():all_predictors()) %>%
  prep(verbose = TRUE, log_changes = TRUE)
```

```{r}
enet_wflow <- workflow() %>% 
  add_model(enet_spec) %>% 
  add_recipe(p3_m5_recipe)

lasso_fit <- enet_wflow %>% 
  update_model(linear_reg(penalty = 0.1, mixture = 1) %>% 
                 set_engine("glmnet",
                            intercept = TRUE, standardize.response = TRUE, standardize = TRUE,
                            path_values = exp(seq(-10.5, 2, length.out = 75)))) %>% 
  fit(ef_df)

lasso_fit %>% extract_fit_parsnip() %>% 
  pluck("fit") %>% 
  plot(xvar = 'lambda')
```

```{r}
if(parallel::detectCores(logical=FALSE) > 3){
  library(doParallel)
  
  num_cores <- parallel::detectCores(logical=FALSE)
  cl <- makePSOCKcluster(num_cores - 2)
  registerDoParallel(cl)
}
```

```{r}
start_enet <- Sys.time()

enet_res <- tune_grid(
  enet_wflow,
  resamples = cv_folds,
  grid = enet_grid,
  metrics = my_metrics
)

finish_enet <- Sys.time()

finish_enet - start_enet
```

```{r}
enet_res %>% autoplot() +
  theme_bw() +
  theme(legend.position = "top")
```

```{r}
enet_res %>% readr::write_rds("Part3_model5_reg.rds")
re_load_mod6_bayesian <- readr::read_rds("Part3_model5_reg.rds")
re_load_mod6_bayesian %>% summary()
```



